\subsection{Purpose}
This document aims to detail the design of the software and of the architecture regarding the system of Travlendar+.
To do so it will be taken a more detailed approach for the description of each component and the overall architecture of the system, by also pointing out the relations between each module and giving a description of such relationships.

\subsection{Scope}
Travlendar+ is a time/travel management web-based system, designed to help the users to keep track of their daily routine by scheduling for them the best way to move from one place to the other using all the information given by the users themselves and external data in order to deliver a tailored experience for everyone.\\
After the user enters all the needed data to register an event, the system will automatically alert him/her when it’s time to leave and will give directions to reach each one of the means of travel as specified in the options, taking into account also factors like the weather and possible public transportation strikes.

\subsection{Definitions, Acronyms, Abbreviation}
\begin{itemize}
\item DD : Design Document
\item RASD: Requirement Analysis and Specification Document
\item API: Application Programming Interface
\item DB: DataBase
\item DBMS: DataBase Management System
\item GPS: Global Position System
\item ER: Entity Relation Model
\end{itemize}

\subsection{Revision History}

\subsection{Reference Documents}
\begin{itemize}
\item Document of the assignment: Mandatory Project Assignments.pdf
\item Requirements and Specification Document
\end{itemize}

\subsection{Document Structure}
This document is structured has:
\begin{enumerate}
	\item \textbf{Introduction}, it provides an overview of the entire document.
	\item \textbf{Architectural Design}, it describes different views of components and their interaction.
	\item \textbf{Algorithm Design}, it describes the main algorithms of the application.
	\item \textbf{User Interface Design}, it provides an overview about the aspect of the user interfaces of the system.
	\item \textbf{Requirements Traceability}, it describes how the requirements described in RASD document maps with components described in this document.
	\item \textbf{Implementation, Integration and Test Plan}, it describes the orders in which the components are implemented and the order of the integration.
	\item \textbf{Appendix}, it contains software used and effort spent.
\end{enumerate}



